The Effects of Weather on Maize Yields: New Evidence from Kenya

### 2018-12-03 writing/draft3/draft3.tex
working hardly
formating figure

  \begin{figure}
   \includegraphics{marginalEffects.pdf}
\caption{Marginal effects of seasonal rainfall and temperature}\label{bar}
\end{figure}

>>>>

  \begin{figure}
   \includegraphics{Figure1a_1f.pdf}\label{bar}
\caption{Predicted marginal effects of seasonal precipitation (left column) and average seasonal temperature (right column) on maize yields. The first row (a, b) represents the model for all counties, the second row (c, d) is based on the subsample of arid and semi-arid counties (ASAL) and the third row (e, f) represents the model for the non-ASAL counties. Precipitation and temperature (x-axis) are in multiples of their standard deviations.}
\end{figure}
